---
title: "Exploring Survival on the Titanic"
author: "Md Aminur Rahman - s3795270"
date: 'Last updated: Sunday, June 02, 2019'
output:
  slidy_presentation:
    df_print: paged
    font_adjustment: 0
    highlight: haddock
    mathjax: default
  ioslides_presentation:
    highlight: haddock
  beamer_presentation:
    highlight: haddock
subtitle: Subtitle Comes Here
---

```{r setup, include=FALSE}
# Use this chunk to quietly load your pacakges

knitr::opts_chunk$set(
	fig.align = "center",
	message = FALSE,
	warning = FALSE
)
# Packages loaded in this chunk will not appear in the presentation. 

library(ggplot2) # Useful for creating plots
library(dplyr)  # Useful for data maipulation
library(knitr) # Useful for creating nice tables

```



# RPubs link information

Rpubs link comes here: http://rpubs.com/aminbuet/titanic


# Introduction
 I have choosen TITANIC dataset from kaggle to analysis and investigate. The detalis of the datsets you can look at https://www.kaggle.com/mrisdal/exploring-survival-on-the-titanic/data

# Problem Statement

- Try to predict who is survived when it sank.
- I use graph to clearly visulize the propability of survival.

# Data

-I downloaded data to my working directory fromfolllowing link https://www.kaggle.com/c/titanic/data
```{r}
# Setting working directory
setwd("~/Documents/RMIT/Semester01/Statistics/Assignment3")

# load Data
train <- read.csv("~/Documents/RMIT/Semester01/Statistics/Assignment3/data/train.csv")
test <- read.csv("~/Documents/RMIT/Semester01/Statistics/Assignment3/data/test.csv")

# Combine two sets
combined <- bind_rows(train, test)

# Check data
str(combined)
```


# Data Cont.

We've got a sense of our variables, their class type, and the first few observations of each. We know we're working with 1309 observations of 12 variables. To make things a bit more explicit since a couple of the variable names aren't 100% illuminating, here's what we've got to deal with:

Variable Name | Description
--------------|-------------
Survived      | Survived (1) or died (0)
Pclass        | Passenger's class
Name          | Passenger's name
Sex           | Passenger's sex
Age           | Passenger's age
SibSp         | Number of siblings/spouses aboard
Parch         | Number of parents/children aboard
Ticket        | Ticket number
Fare          | Fare
Cabin         | Cabin
Embarked      | Port of embarkation

# Descriptive Statistics and Visualisation

```{r}
# How many survived?
barplot(table(train$Survived),
        names.arg = c("Perished", "Survived"),
        main="Survived (passenger fate)", col="black")
```
```{r}
# Passengers travelling in different classes
barplot(table(train$Pclass), 
        names.arg = c("first", "second", "third"),
        main="Pclass (passenger traveling class)", col="firebrick")
```
```{r}
# How many survived gender-wise?
barplot(table(train$Sex), main="Sex (gender)", col="darkviolet")
```
```{r}
# Age distribution in the Titanic
hist(train$Age, main="Age", xlab = NULL, col="brown")
```
```{r}
# How in group people (sibling+spouse) were traveling?
barplot(table(train$SibSp), main="SibSp (siblings + spouse aboard)", col="darkblue")
```
```{r}
# How parents and children were traveling? 
barplot(table(train$Parch), main="Parch (parents + kids aboard)", col="gray50")
```
```{r}
# What was the fair most people paid for Titanic?
hist(train$Fare, main="Fare (fee paid for ticket[s])", xlab = NULL, col="darkgreen")
```
```{r}
# Where most people Embarked?
barplot(table(train$Embarked), names= c("Missing", "Cherbourg", "Queenstown", "Southampton"), 
        main="Port of Embarkation")
```

# Decsriptive Statistics Cont.

- You can use the `knitr:kable` function to print nice HTML tables. Here is an example R code:

```{r}
combined %>% group_by(Sex) %>% summarise(Min = min(Age,na.rm = TRUE),
                                           Q1 = quantile(Age,probs = .25,na.rm = TRUE),
                                           Median = median(Age, na.rm = TRUE),
                                           Q3 = quantile(Age,probs = .75,na.rm = TRUE),
                                           Max = max(Age,na.rm = TRUE),
                                           Mean = mean(Age, na.rm = TRUE),
                                           SD = sd(Age, na.rm = TRUE),
                                           n = n(),
                                           Missing = sum(is.na(Age))) -> table1
knitr::kable(table1)
```
```{r}
# Fill in Age NAs
library(rpart)
summary(combined$Age)

FillAge <- rpart(Age ~ Pclass + Sex, 
                data=combined[!is.na(combined$Age),], method="anova")
combined$Age[is.na(combined$Age)] <- predict(FillAge, combined[is.na(combined$Age),])
summary(combined)

```


# Hypothesis Testing

- Apply an appropriate hypothesis test for your investigation. 
- Ensure you state and check any assumptions. 
- Report the appropriate values and interpret the results.
- Here is an example:

```{r}
model1 <- lm(Age ~ Sex, data = combined)
model1 %>% summary()
```


# Discussion

The major findings of my investigatios are -
- Most of the passengers were died.
- More than half passengers were in #rd class , greater than (1st Classs + 2nd Class).
- Male passengers were more.
- Single passangers were more.
- Most of the fare around $80.
- Most of the passenger embarked from Southampton.

# References

 I read and try understand different from Kernels of kaggle, classnotes and course materials.